---
title: "BDA - Project Work"
subtitle: "Metro Interstate Traffic Volume"
author: "Otso Hellman & Henri Lencioni"
output: 
  pdf_document: 
    toc: yes
    toc_depth: 1
---

```{r setup, include=FALSE}
# This chunk just sets echo = TRUE as default (i.e. print all code)
knitr::opts_chunk$set(echo = TRUE)
```


# Loaded packages

Here we introduce the packages used in the notebook. Please remember to install them in case they have not been used previously on the computer.

```{r, echo=FALSE}
library(ggplot2)
```

# Description of the data

Please access the data [here](https://archive.ics.uci.edu/ml/datasets/Metro+Interstate+Traffic+Volume). The data has to be unzipped and after the workspace has been fixed, we can access the data.

```{r}
data = read.csv("Metro_Interstate_Traffic_Volume.csv")
summary(data)
```
Here we can see a quick summary of the data. We have a total of 48 204 observations with 9 variables. The problem setting is to estimate traffic volume based on the first 8 variables. Furthermore, from a quick summary we can see some problems. There are some zero values in temperature, even though the normal temperature should be around 270 and up.

```{r}
data$temp[data$temp == 0] <- mean(data$temp)
p <- ggplot(data, aes(x=temp)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white") +
 geom_density(alpha=.2, fill="#FF6666") 
p + geom_vline(aes(xintercept=mean(temp)),
            color="blue", linetype="dashed", size=1)
```
# Description of models used

# Description of prior choices

# Stan implementations

# Convergence diagnostics

# Posterior predictive checking

# Model comparison

# Predictive accuracy

# Sensitivity analysis

# Problem setting and potential improvements